---
title: "Alcohol vs Seat choice"
author: "Leslie Johnson"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

It appears that the back row is higher than the front and the middle.

### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

In this boxplot, we can see the difference that the box in the back row is slightly bigger than the first boxplot we observed above.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The back row is extremely different because their mean is 9.6, the middle row is only 3.2, and the front row has a low mean of 1.8.


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We will reject this null hypothesis, but we will seek clarification on the differences of each of row. 


```{r}
plot(TukeyHSD(model1))
```

Using the Turkey boxplot we can tell the front and the middle is different from the back, but there is no difference between the middle and the front.


## Conclusions


